article title

### 2022-07-25 pilon_gilles_glossary.tex
Add average chart
Add parallelism chart

@@

@@

    description={It is a chart that plots the range of a subgroup of values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line, and an average line.},

>>>>

\newglossaryentry{average_chart}
    name={average chart},
    description={It is a process behaviour chart that plots the average of a subgroup of values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line and an average line.},
    plural={average charts}

@@

\newglossaryentry{parallelism_chart}
    name={parallelism chart},
    description={It is a process behaviour chart that plots the lines from the average chart and puts them on top of each other. It is used in measurement system analysis. Differences for any part indicate an operator bias relative to other operators.},
    plural={parallelism charts}

@@

    description={It is a process behaviour chart that plots the range of a subgroup of values taken in a rational manner. The chart also has an upper control limit line, a lower control limit line, and an average line.},
